Deep Learning for Automatic Speech Recognition

### 2015-04-21 Presentation/Presentation.tex
typos
Remainder of presentation slides
Filled in remaining experiments and conclusion slides.

	\hfill George Dahl \hfill Dong Yi \hfill Li Deng \hfill Alex Acero \hfill

@@

\begin{frame}{Problem Formulation (Cont)}
	\begin{center}
	Here the acoustic model is viewed as a sequence of transitions between states of tied-state triphones referred to as \textbf{senones}.
	\end{center}

@@

\begin{frame}{Deep Neural Networks}
	\resizebox{\linewidth}{!}{\includegraphics{dnn.pdf}}
\end{frame}

\begin{frame}{Training}
	\begin{center}
		Training is complicated and time intensive! At a very high level two steps: initialization and DNN training.
	\end{center}

@@

\begin{frame}{Training}

@@

\begin{frame}{Pre-Training In-Depth}
	\vfill

@@

	\begin{center}
		Need to understand Restricted Boltzman Machines (RMBs) and Deep Belief Networks (DBNs)
	\end{center}

@@

\begin{frame}{Pre-Training: RBMs and DBNs}
	\vfill

@@

\begin{frame}{Pre-Training: Contrastive Divergence}
		\begin{center}
			Want to do vanilla Stochastic Gradient Descent, however, our \textcolor{blue}{model} term takes \textbf{exponential} time to compute correctly. 
		\end{center}

@@

		\begin{center}
			Instead, \textbf{approximate} it (essentially minimizing Kullback-Leibler divergence) with \textcolor{blue}{one step} Gibbs sampling:
		\end{center}

@@

\begin{frame}{Pre-Training: Bringing it all together}
	\begin{columns}
		\begin{column}{0.45\linewidth}
			Hinton's Greedy Algorithm:

@@

\begin{frame}{Experimental Results}

\begin{table}[H]
	\begin{center}
		Papers report different metrics (sentence accuracy, phone error rate) on different datasets (Bing, TIMIT) 
	\end{center}

@@

	\centering
	\begin{tabular}{c|c|c|c|c}
		& \multicolumn{2}{c|}{Bing Mobile} & \multicolumn{2}{c}{TIMIT}\\
		Architecture & Dev. & Test  & Dev. & Test \\
		\hline
		CD-GMM-HMMM & 70.3\% & 68.4\% & & \\
		CD-DNN-HMM & 71.8\% & 69.6\% & & \\
		\hline
		CNN-HMM  & & &  & 20.07\%
	\end{tabular}

@@

	\begin{center}
		Take away: Both demonstrate significant improvement over GMM approach, with CNN approach giving the best performance.
	\end{center}
\end{table}

@@

\begin{frame}{Conclusions}
	\TODO{Garrett}
\end{frame}

\begin{frame}{Conclusions (Cont)}
	\TODO{Garrett}
\end{frame}

>>>>

	 $ $ \hfill George Dahl \hfill Dong Yi \hfill Li Deng \hfill Alex Acero \hfill  $ $

@@

\begin{frame}{Problem Formulation (cont.)}
	\begin{center}
	Here the acoustic model is viewed as a sequence of transitions between states of tied-state triphones referred to as \textbf{senones}.
	\end{center}

@@

\begin{frame}{Problem Formulation (cont.)}
	\resizebox{\linewidth}{!}{\includegraphics{dnn.pdf}}
\end{frame}

\begin{frame}{CD-DNN-HMM Training}
	\begin{center}
		Training is complicated and time intensive! At a very high level two steps: initialization and DNN training.
	\end{center}

@@

\begin{frame}{CD-DNN-HMM Training (cont.)}
	\vfill

@@

\begin{frame}{DNN Pre-Training In-Depth}
	\vfill

@@

	\begin{center}
		Need to understand Restricted Boltzmann Machines (RBMs) and Deep Belief Networks (DBNs)
	\end{center}

@@

\begin{frame}{DNN Pre-Training: RBMs and DBNs}
	\vfill

@@

\begin{frame}{DNN Pre-Training: Contrastive Divergence}
		\begin{center}
			Want to do vanilla Stochastic Gradient Descent, however, our \textcolor{blue}{model} term takes \textbf{exponential} time to compute correctly. 
		\end{center}

@@

		\begin{center}
			Instead, \textbf{approximate} it with \textcolor{blue}{one step} Gibbs sampling (essentially minimizing Kullback-Leibler divergence):
		\end{center}

@@

\begin{frame}{DNN Pre-Training: Bringing it all together}
	\begin{columns}
		\begin{column}{0.45\linewidth}
			Hinton's Greedy Algorithm:

@@

\begin{frame}{Experimental Results}
	\vfill

	Metrics
	\begin{itemize}
		\item Sentence Error Rate (SER): Incorrect sentences (at least one word wrong) out of total sentences.
		\item Word Error Rate (WER): Levenshtein based measure of number of substitutions, deletions, and insertions relative to total words.
		\item Phoneme Error Rate (PER): Incorrect phonemes out of total phonemes
	\end{itemize}

\begin{frame}{Experimental Results (cont.)}
	\vfill

	Datasets
	\begin{itemize}
		\item Bing Mobile: Corpus of Siri-like spoken questions.
		\item TIMIT: Corpus from Texas Instruments and Massachusetts Institute of Technology. 630 speakers.
		\item Switchboard: Corpus from Texas Instruments in 1990. Telephone conversations. 543 speakers.
	\end{itemize}

@@

	\begin{center}
		See Linguistic Data Consortium for TIMIT and Switchboard.
	\end{center}

\begin{frame}{Experimental Results}
	\begin{center}
		Hinton et al. \textit{Deep Neural Networks for Acoustics Modeling in Speech Recognition: The shared views of four research groups} 
	\end{center}

@@

	\begin{table}[H]
		\centering
		\begin{tabular}{c|c|c|c}
			& Switchboard & Bing Mobile & TIMIT \\
			& (WER) & (SER) & (PER) \\
			\hline
			GMM & 23.6 & 36.2 & 21.7 \\
			DNN & 16.1 & 30.4 & 21.9 \\
			CNN & $-$ & $-$ & 20.2 \\
			\hline
			RNN & $-$ & $-$ & 17.7
		\end{tabular}
	\end{table}

	\begin{center}
		Takeaway: ANN-based methods perform better than the established GMM approach on multiple datasets and error metrics.
	\end{center}
\end{frame}

@@

\begin{frame}{Conclusions}
	\vfill

	\begin{center}
		Neural Networks are promising alternative to GMMs for acoustic modeling in ASR. But they have computational limitations \newline (e.g., not easily parallelizable across clusters)
	\end{center}

	\begin{center}
		These techniques are in play at Baidu, Google, and Microsoft. No word on Pearson, Nuance, Apple.
	\end{center}

	\begin{center}
		Our money on CNNs. They can do more with less (Better results with fewer nodes). Though Hinton critical of the approach.\newline
		(\textit{What's wrong with convolutional nets?} MIT 2014)
	\end{center}
